\documentclass[11pt,a4paper,draft]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{xcolor}
%\usepackage{showframe} %This line can be used to clearly show the new margins

\newgeometry{vmargin={30mm}, hmargin={35mm,25mm}} 

\begin{document}
\textbf{Response Reviewer 2}

\textbf{
	Interactive comment on ``Can machine learning
	correct microwave humidity radiances for the
	influence of clouds?'' by Inderpreet Kaur et al.}

\begin{itemize}

\item 			
			As I understand it, this study uses only simulated measurements (either with or without hydrometeors included), even for MWHS-2 for which actual measurements are available. This should be made clearer, especially given line 66, which states that no``background'' data is required for the method. I'd also like to see a bit more discussion 	about whether the results you present should be expected to hold for real data. An assumption that you are making is that your forward model can represent real clouds with enough fidelity that a model trained on simulated data will still work on real-world data. Can you point to any evidence to back up this assumption? Have you tried comparing the histograms of model-simulated Tbs with real-world MWHS-2 Tbs?

\textcolor{blue}{Reply: We agree with the reviewer, the line 66, can be confusing. We have rearranged the text to give clarity.
Regarding the the discussion about simulations holding well for the real-data, we have added a new subsection () under Discussion.
Also, MWHS-2 simulations used in the study are the background radiance simulated by ECMWF for their assimilation systems. Their observational error model is already described in literature e.g. Lawrence et al., 2015. }

		
\item  	
			What is the computational cost of the QRNN method compared to simpler cloud-
			clearing filters? Could it feasibly be implemented into existing NWP models given
			current computational constraints?

\textcolor{blue}{Reply: \textcolor{red}{add time} Yes, it would be feasible to implement the scheme into existing NWP models. It should be noted QRNN was not optimized to get the maximum computational performance. However, with the modern computing architectures a much faster computation can be expected. }

\item  
			Lines 135-143: Why the large difference in number of cases simulated for ICI (220,000)
			vs. AWS (143,000), if they are both coming from the same population of CloudSat
			profiles? For the training dataset, you use about 75\% of total cases for MWHS-2,
			about 80\% of cases for ICI, and about 84\% of cases for AWS. Why this difference in
			proportions?

\textcolor{blue}{Reply: Yes, both ICI and AWS simulations come from same population of Cloudsat. For SMS, we had access to a smaller database, which was used for a earlier study. Due to difference in sizes of the available observations, maximum possible observations were incorporated to allow  representation to each cloud event. Even with differences in the database sizes, the results show that the predicted quantiles are well calibrated for all three sensors. With a larger database, one could expect similar or even better performance.}

\item  
			Line 340: ``With a test dataset of 70 000 samples, we cannot represent the far wings of the distribution accurately.'' Couldn't one apply this same reasoning to Figures 2,3, or
			8, which have density values below $10^{-4}$ included?

\textcolor{blue}{Reply: Yes one could apply the same reasoning to the Figures 2, 3, or 8, but we prefer to show the complete distribution to emphasize that the cases with large errors occur infrequently. \textcolor{red}{Shall we show the complete dist?}}


\item 
			Figure 13: I wonder if there might be an easier, more concise way to evaluate whether
			the uncertainty intervals are properly calibrated. Namely, could you simply calculate
			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot? If this percentage is significantly less than 95\%, it would suggests that your uncertainties are too small, while if it were closer to 100\% it would suggest your uncertainties are too large. Even if you don't get rid of Fig. 13, I think this would be useful information to include in the paper.

\textcolor{blue}{Reply: As per suggestion of the reviewer, we have included the information highlighting how well calibrated the uncertainties are. We add this information in Fig. 13. We provide the occurence percentage of true value for each uncertainty bin. We would also like to point out that Fig.6 and Fig.10 already show the calibration of uncertainty intervals, but this additional information reinforces the results further.} 

\item  
			Lines 498-499: ``. . . other underlying uncertainties not considered here.'' Whether here or elsewhere in the paper, I think you should talk a bit more about what these other uncertainties are (radiative transfer model errors should certainly be discussed), and what effects they might have on your results.

\textcolor{blue}{Reply:}

\end{itemize}
	
\textbf{Typos}
\begin{itemize}


\item Line 26: The phrase ``weather satellites are since some time equipped'' is confusing to
me. I suggest ``weather satellites have for some time been equipped. . .''

\textcolor{blue}{Reply: The sentence is re-written as per suggestion.}

\item Line 51: I believe you are missing the word ``on'' between ``predicated'' and ``Gaussian.''

\textcolor{blue}{Reply: The typo is corrected.}

\item Line 154: Should 85\% be changed to 84\%? That would be +2 sigma for a normal
distribution.

\textcolor{blue}{Reply: Yes, the predicted percentile should be 84\% instead of 85\%. The typo is corrected.} 


\item Line 455:``. . . provide coverage to the humidity channels in, lower and mid troposphere''
This is confusing - get rid of the comma and add the word ``the'' instead?

\textcolor{blue}{Reply: The comma is removed and the word ``the'' is added.}


\item Line 494:	``QRNN predictions are weighted mean. . .'' I think this should say, ``QRNN
predictions are the weighted mean. . .''

\textcolor{blue}{Reply: The word ``the'' is added.}



\item Line 508: Missing ``the'' before ``same''


\textcolor{blue}{Reply: The word ``the'' is added.}

\end{itemize}
	
\end{document}